% options:
% thesis=B bachelor's thesis
% thesis=M master's thesis
% czech thesis in Czech language
% english thesis in English language
% hidelinks remove colour boxes around hyperlinks

\documentclass[thesis=B,english,hidelinks,table,12pt]{template/FITthesis}[2019/12/23]
\OnehalfSpacing
\raggedbottom % no huge vertical whitespace between elements on short pages

\usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
% \usepackage[latin2]{inputenc} % LaTeX source encoded as ISO-8859-2
% \usepackage[cp1250]{inputenc} % LaTeX source encoded as Windows-1250

% \usepackage{subfig} % subfigures
% \usepackage{amsmath} % advanced maths
% \usepackage{amssymb} % additional math symbols

% empty lines between paragraphs
\setlength{\parindent}{0pt}
\abnormalparskip{\baselineskip}

\usepackage{dirtree} % directory tree visualisation
\usepackage[T1]{fontenc} % 8-bit font encoding
\usepackage[hypcap=true]{caption} % fix for figure and table label positioning in PDF
\captionsetup[figure]{belowskip=-\baselineskip} % fix for too much space when combined with \abnormalparskip

% list page breaks and margins
\usepackage{enumitem}
\newlength\docparskip
\setlength{\docparskip}{\parskip}
\setlist[1]{before={\parskip=0pt},after={\vspace{-\docparskip}}}
\setlist{beginpenalty=10000}

% pretty printing source code
\usepackage[outputdir=auxil]{minted}
\setminted{autogobble=true,tabsize=4,fontsize=\footnotesize}

% quotes style
\usepackage[vskip=0pt,rightmargin=0pt]{quoting} % block quotes
\usepackage[autostyle,english=american]{csquotes} % inline quotes
\MakeOuterQuote{"}

% glossaries
\usepackage[acronym,nonumberlist,toc,numberedsection=autolabel,docdef=restricted]{glossaries-extra}
\makeglossaries
\glssetcategoryattribute{general}{glossdesc}{firstuc}
\setabbreviationstyle[acronym]{long-short}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% EDIT THIS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % %

\department{Department of Software Engineering}
\title{FIDO2 KeePass Plugin}
\authorGN{Martin} % author's given name/names
\authorFN{Kolárik} % author's surname
\author{Martin Kolárik} % author's name without academic degrees
\authorWithDegrees{Martin Kolárik} % author's name with academic degrees
\supervisor{Ing. Jiří Dostál, Ph.D.}
\placeForDeclarationOfAuthenticity{Prague}

\acknowledgements{I would like to thank my supervisor Ing. Jiří Dostál, Ph.D.
for his interest in this topic and the provided support.}

\abstractEN{This thesis explores the possibilities of using FIDO2 devices as a replacement for master passwords
in password managers. It describes the capabilities and current limitations of FIDO2, specifies
the design goals that the final implementation should meet, and discusses four implementation approaches.
In the implementation chapter, it continues to further describe the chosen approach, architectural decisions,
and the encountered challenges. The final part is testing, which verifies that the design goals were met.
As a whole, the thesis is a useful reference for anyone attempting to utilize FIDO2 in password managers
or similar environments.}

\abstractCS{Táto práca skúma možnosti využitia FIDO2 zariadení ako náhradu pre hlavné heslo v správcoch
hesiel. Popisuje možnosti a obmedzenia FIDO2, určuje hlavné charakteristiky, ktoré by výsledná implementácia
mala spĺňať a diskutuje štyri postupy implementácie. V implementačnej časti ďalej popisuje zvolený postup,
architektonické rozhodnutia a objavené problémy. Finálnou časťou je testovanie, ktoré overuje, že implementácia
spĺňa predtým stanovené ciele. Ako celok je táto práca užitočným zdrojom informácií pre kohokoľvek pokúšajúceho
sa využiť FIDO2 v správcovi hesiel alebo podobnom prostredí.
}

\keywordsCS{FIDO2, WebAuthn, KeePass, správca hesiel, bezpečnostný kľúč, prihlásenie bez hesla}
\keywordsEN{FIDO2, WebAuthn, KeePass, password manager, security key, passwordless login}
\declarationOfAuthenticityOption{1} % select as appropriate, according to the desired license (integer 1-6)
\website{https://github.com/MartinKolarik/KeePassFIDO2} % optional thesis URL

% Loaded inside \AtBeginDocument so that autoquotes work: https://tex.stackexchange.com/questions/430111/glossaries-and-csquotes-how-to-use-autoquotes-in-gls-description
\AtBeginDocument{
\input{glossaries/acronyms}
\input{glossaries/glossary}
}

\begin{document}
	\setsecnumdepth{part}

	\chapter{Introduction}\label{ch:introduction}
	\input{content/introduction}

	\setsecnumdepth{all}

	\chapter{State-of-the-art}\label{ch:state-of-the-art}
	\input{content/state-of-the-art}

	\chapter{Analysis and design}\label{ch:analysis-and-design}
	\input{content/analysis-and-design}

	\chapter{Implementation}\label{ch:implementation}
	\input{content/implementation}

	\chapter{Testing}\label{ch:testing}
	\input{content/testing}

	\setsecnumdepth{part}

	\chapter{Conclusion}\label{ch:conclusion}
	\input{content/conclusion}

	\bibliographystyle{template/iso690}
	\bibliography{mybibliographyfile}

	\setsecnumdepth{all}
	\appendix

	\setglossarystyle{alttree}
	\glsfindwidesttoplevelname[acronym]
	\printglossary[type=acronym]

	\glossariesextrasetup{postdot}
	\setglossarystyle{altlist}
	\printglossary

	\chapter{Contents of the enclosed SD card}\label{ch:contents-of-the-enclosed-sd-card}

	\begin{figure}
		\dirtree{%
			.1 README.md\DTcomment{contents description}.
			.1 KeePassFIDO2-v1.0.0.zip\DTcomment{plugin binaries}.
			.1 DeviceCommunicator\DTcomment{source code of the communicator module}.
			.1 KeePassPlugin\DTcomment{source code of the plugin}.
			.1 Thesis\DTcomment{\LaTeX{} source code of the thesis}.
			.2 BP\_Kolárik\_Martin\_2020.pdf\DTcomment{PDF version of the thesis}.
		}
	\end{figure}
\end{document}
